 

### 2021-07-10 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

It is noteworthy that $T_{leaf}$ often differs substantially from that of branches and stems. 
For instance, exposed tropical tree bark can be much warmer than leaves and flowers [@pauTropicalForestTemperature2018]. 
Thus, the vegetation temperature ($T_{veg}$) measured using sensors that integrate across both leaves and woody vegetation (e.g., infrared sensors for $T_{veg}$ at NEON sites, Fig. `r fig_NEON_vertical`h) does not always equal $T_{leaf}$, particularly in settings where leaf area is low relative to woody vegetation (*i.e.*, low-LAI ecosystems and understories). 
Recent advances in $T_{leaf}$ modeling (see "Scaling across Space and Time") will enhance our understanding of large scale $T_{leaf}$ vertical patterns [@stillImagingCanopyTemperature].

>>>>

It is noteworthy that $T_{leaf}$ often differs substantially from that of branches and stems; for instance, exposed tropical tree bark can be much warmer than leaves and flowers [@pauTropicalForestTemperature2018]. 
Thus, the vegetation temperature ($T_{veg}$) measured using sensors that integrate across both leaves and woody vegetation (e.g., infrared sensors for $T_{veg}$ at NEON sites, Fig. `r fig_NEON_vertical`h) does not always equal $T_{leaf}$, particularly in settings where leaf area is low relative to woody vegetation (*i.e.*, low-LAI ecosystems and understories). 
Recent advances in $T_{leaf}$ modeling (see "Scaling across Space and Time") will enhance our understanding of large scale $T_{leaf}$ vertical patterns [@stillImagingCanopyTemperature].
